Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-06-21 paper/ms.tex
additional paragraphs

Imposing additional constraints with the maximal number of consistent
mock surveys and the angular correlation function we end up with 50
models out of the original 90000 models. In what follows we discuss
the implications of the selection of these models on the escape
fraction of Lyman $\alpha$ radiation, the stellar abundance and the
star formation efficiency in LAEs at $z=3.1$.

\subsection{Escape fraction}

We find that the majority ($80\%$) of the best models have a low
ocacupation fraction $f_{\rm occ}\leq 0.4$. This preference goes in
the same direction as the observational constraint on $f_{\rm occ}\sim
0.1-0.2$ derived at $z=2.2$ by \cite{Hayes2010}.

Their estimation was based on blind surveys of the H$\alpha$ and Lyman $\alpha$ line with the
European Southern  Observatorio (ESO) Very Large Telescope
(VLT). Using corrections by extinction to obtain an estimate for the
intrinsic H$\alpha$ luminosity, and using values for the theoretical
expectation of the ratio Lyman$\alpha$/H$\alpha$ they derive an bulk escape fraction for
the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
esc}=(10.7\pm 2.8)\%$ if a different dust correction is used. The
authors show that the luminosity function for LAEs at $z=2.2$ is
consistent with the escape fraction being constant for every galaxy
regardless of its luminosity. From this results they derive that
almost $90\%$ of the star forming galaxies emit insufficient
Lyman $\alpha$ to be detected, effectively setting the occupation
fraction to be $f_{\rm occ}=0.10$. For the cosmological parameters
used in this \documentname the age of the universe between $z=3.1$ and
$z=2.2$ has changed by $\sim 1$ Gyr. We assume that the physical
conditions that determine the escape fraction $f_{\rm esc}$ and the
occupation fraction $f_{\rm  occ}$ remain similar over that time
scale.

Including the information of the halo mass range size allows us

These 50 models can be classified into two families of the same
size.

The first, where the range $M_{\rm min}-M_{\rm max}$ is narrow,
typically of less than $<1.0$ dex. While in the second familiy the
extent $>1.0$ dex. In the first case the minimum halo mass is found to
be in a wide range $10^{10}\hMsun <M_{\rm min}< 10^{11.5}\hMsun$ while
in the second case, only models with $M_{\rm min}\sim 10^{10.9}\hMsun$
are compatible with the observational contraints. In what follows we
discuss the implications of the existence of these two families of
models.

When we additional include the ACF constraint we find that only models with 
$\log_{10}M_{\rm min}\leq 11.0$ and $\log_{10}M_{\rm max}\leq 12.0$ 
are now consistent with observations.

Including all the observational constraints we find that only between $15$ to $20$ 
models reproduces observations. The list for the model parameters is in the
Appendix in Table \ref{table:models_match}.

\subsection{Implications for galaxy formation models}

>>>>

Imposing additional constraints with the maximal number of consistent
mock surveys and the angular correlation function we end up with 50
models out of the initial 90000 models. In what follows we discuss
the implications of the selection of these models on the escape
fraction of Lyman $\alpha$ radiation, the stellar abundance and the
star formation efficiency in LAEs at $z=3.1$.

\subsection{Escape fraction and allowed halo mass range}

We find that the majority ($70\%$) of the best models have a low
ocacupation fraction $f_{\rm occ}\leq 0.3$. This preference goes in
the same direction as the observational constraint on $f_{\rm occ}\sim
0.1-0.2$ derived at $z=2.2$ by \cite{Hayes2010} and recent theoretical
study of observational data in a wide redshift range $0<z<6$ by
\cite{Dijkstra2013}.

The observational estimation by \cite{Hayes2012} was based on blind
surveys of the H$\alpha$ and Lyman $\alpha$ line. Using corrections by
extinction to obtain an estimate for the intrinsic H$\alpha$
luminosity, and using values for the theoretical expectation of the
ratio Lyman$\alpha$/H$\alpha$ they derive an bulk escape fraction for
the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
  esc}=(10.7\pm 2.8)\%$ if a different dust correction is used.

They also showed that that the luminosity function for LAEs at $z=2.2$ is
consistent with the escape fraction being constant for every galaxy
regardless of its luminosity. From this results they derive that
almost $90\%$ of the star forming galaxies emit insufficient
Lyman $\alpha$ to be detected, effectively setting the occupation
fraction to be $f_{\rm occ}=0.10$.

The results by \cite{Dijkstra2013} use a similar principle. They
compared observationally dereived star formation functions to LAE
luminosity functions. At $z\sim 3.0$ they derive an affective escape
fraction of $f_{\rm esc}=(17\pm 5)\%$, which in turn using the same
arguments in \cite{Hayes2010} could be interpreted as an occupation
fraction $f_{\rm occ}\sim 0.2$.  We consider a sucess of our method
the fact that we find that most of the consistent models show a low
occupation fraction.

The study of the escape farction is also complementary to the size of
the halo mass range $\Delta M=\log_{10}M_{\rm max} - \log M_{\rm
  min}$for LAEs. All the successful model we have found can be 
split into three families. 
\begin{itemize}
\item[(1)] Low $f_{\rm occ}\leq 0.3$ and low $\Delta M\leq 1.0$
  dex: 24 models.
\item[(2)] High $f_{\rm occ}> 0.3$ and low $\Delta M\leq 1.0$: 14 models
\item[(3)] Low $f_{\rm occ}\leq 0.3$ and high $\Delta M > 1.0$dex: 11
  models
\end{itemize}

There is a clear majority of models with a narrow $\Delta M\leq
1$, such models imply that there is a cut for lower and higher halo masses
that render inefficient the presence and/or detection of LAEs.  A cut
a lower masses can be readily interepreted in terms of the minimal halo star
formation rate needed to produce the necessary \lya luminosity to be
above a given detection threshold.

The cut at higher halo masses requires a different explanation. A
possible interpretation can be made in terms of a lower escape
fraction of \ly radiation in massive systems. There are detailed models for
radiative transfer that support the idea that massive galaxies with
higher metallicities have larger dust contents than lower mass
systems, which due to the resonant nature of the \ly line are enough
to produce high absorption of \ly photons but not of continuum or
other non-resonant lines.

This preference for narrow $\Delta M$ ranges for hosting LAEs together
with the total absence of reasonable models with $M_{\rm max}>
10^{12}$\hMsun shows that our models supports theoretical insights
where the most massive systems are not bright \ly sources.

%The first, where the range $M_{\rm min}-M_{\rm max}$ is narrow,
%typically of less than $<1.0$ dex. While in the second familiy th
%extent $>1.0$ dex. In the first case the minimum halo mass is found to
%be in a wide range $10^{10}\hMsun <M_{\rm min}< 10^{11.5}\hMsun$ while
%in the second case, only models with $M_{\rm min}\sim 10^{10.9}\hMsun$
%are compatible with the observational contraints. In what follows we
%discuss the implications of the existence of these two families of
%models.  
%When we additional include the ACF constraint we find that only models with 
%$\log_{10}M_{\rm min}\leq 11.0$ and $\log_{10}M_{\rm max}\leq 12.0$ 
%are now consistent with observations.

%Including all the observational constraints we find that only between $15$ to $20$ 
%models reproduces observations. The list for the model parameters is in the
%Appendix in Table \ref{table:models_match}.

\subsection{Models in the context of abundance matching}

The abundance matching methods, whereby a stellar mass is associated
to a halo mass in order to reproduce various luminosity functions, can
be used to interpret the results we have obtained so far.
